Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-12 doc/PRF2022/PRF_main.tex
peter working on tasks

%% ***A*** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}

@@

% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
\bibliographystyle{apsrev4-2}

@@

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}asdf}
\end{figure}
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively. 
In both cases, $\dot \gamma$ is the shear rate.
To obtain a range for $\dot \gamma$, 
consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
the characteristic phase sample radius 
and bending rigidity, respectively. 
That is, $\kappa$ gives the elastic stress 
for restoring the phase-sample shape.
Shear stress overcomes elastic stress   
when $C_a > 1$ and this yields 
$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
Thus our values for $\dot \gamma$ range between 
$0$ ns$^{-1}$ corresponding to quiescent flow
up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
Such shear rates are compatible with molecular dynamics 
simulation \cite{Bradner}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels 
 where shear rates range over 100--1000 s$^{-1}$ \cite{NEEDED}.

@@

To estimate $h(\kk)$, 
the $N_b = 60$ JP
vesicle in Figure \ref{fig:ES2_summary}(e) 
has arc length $L_x \approx 50$ nm. 
Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
Since our simulations are two-dimensional, we restrict our attention
to transversely invariant fluctuations where $n = 0$.
Substituting these values gives 
\begin{equation}
\label{eq:fourier_spectrum_upper}
\langle |h(\kk)|^2 \rangle \approx \frac{4 \text{ nm}^3}{L_y}\frac{1}{m^4}, \quad m = \pm 1, \pm 2, \dots
\end{equation}
For any moderate width, say $L_y > 4$ nm, the leading Fourier coefficient
has an expected magnitude less than $1$ nm with the remaining coefficients
dropping off to zero precipitously.  The expected amplitudes coming from thermal
fluctuation are therefore negligible compared to particle size.
The elastic
moduli for the Type (II) and Type (III) phases are by greater by a factor of two
and five, respectively, than for Type (I) (Figure \ref{fig:F_summary}(c)), making thermal fluctuation
even more negligible in these cases.

>>>>

%% ***A*** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-2}

@@

% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-2}

@@

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}asdf}
\end{figure}
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively. 
In both cases, $\dot \gamma$ is the shear rate.
To obtain a range for $\dot \gamma$, 
consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
the characteristic phase sample radius 
and bending rigidity, respectively. 
That is, $\kappa$ gives the elastic stress 
for restoring the phase-sample shape.
Shear stress overcomes elastic stress   
when $C_a > 1$ and this yields 
$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
Thus our values for $\dot \gamma$ range between 
$0$ ns$^{-1}$ corresponding to quiescent flow
up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
Such shear rates are compatible with molecular dynamics 
simulation \cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels 
 where shear rates range over 100--2000 s$^{-1}$ \cite{Cho2011}.

@@

To estimate $h(\kk)$, 
the $N_b = 60$ JP
vesicle in Figure \ref{fig:s2esummary}(e) 
has arc length $L_x \approx 50$ nm. 
Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
Since our simulations are two-dimensional, we restrict our attention
to transversely invariant fluctuations where $n = 0$.
Substituting these values gives 
\begin{equation}
\label{eq:fourier_spectrum_upper}
\langle |h(\kk)|^2 \rangle \approx \frac{4 \text{ nm}^3}{L_y}\frac{1}{m^4}, \quad m = \pm 1, \pm 2, \dots
\end{equation}
For any moderate width, say $L_y > 4$ nm, the leading Fourier coefficient
has an expected magnitude less than $1$ nm with the remaining coefficients
dropping off to zero precipitously.  The expected amplitudes coming from thermal
fluctuation are therefore negligible compared to particle size.
The elastic
moduli for the Type (II) and Type (III) phases are by greater by a factor of two
and five, respectively, than for Type (I) (Figure \ref{fig:fsummary}(c)), making thermal fluctuation even more negligible in these cases.
